Supplementary Materials- A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-23 analysis/paper/supplementary-material.Rmd
removed characters on the top of MCMC diagnostic plots

  plot(density(x$Theta[, i]), 
       main = "", 
       axes = FALSE, 
       xlab = bquote(paste(theta[.(i)], " (", .(x$specs[i]), ")")),
       ylab = "", lwd = 2)
  axis(1)
  axis(2)
  coda::traceplot(x$Theta[, i], type = "l", xlab = "Iterations", ylab = "")
  coda::autocorr.plot(x$Theta[, i], auto.layout = FALSE)
  if (x$dim > 4) seqq <- seq(4, x$dim, 4)
  if (i %in% union(x$dim, seqq)) {
    title(paste("MCMC output for Model: y ~", x$formula[3]), outer = TRUE)
  }
}

@@

  plot(density(y$Theta[, i]), 
       main = "", 
       axes = FALSE, 
       xlab = bquote(paste(theta[.(i)], " (", .(y$specs[i]), ")")),
       ylab = "", lwd = 2)
  axis(1)
  axis(2)
  coda::traceplot(y$Theta[, i], type = "l", xlab = "Iterations", ylab = "")
  coda::autocorr.plot(y$Theta[, i], auto.layout = FALSE)
  if (y$dim > 4) seqq <- seq(4, y$dim, 4)
  if (i %in% union(y$dim, seqq)) {
    title(paste("MCMC output for Model: y ~", y$formula[3]), outer = TRUE)
  }
}

>>>>

  plot(density(x$Theta[, i]), 
       main = "", 
       axes = FALSE, 
       xlab = bquote(paste(theta[.(i)], " (", .(x$specs[i]), ")")),
       ylab = "", lwd = 2)
  axis(1)
  axis(2)
  coda::traceplot(x$Theta[, i], type = "l", xlab = "Iterations", ylab = "")
  coda::autocorr.plot(x$Theta[, i], auto.layout = FALSE)
  if (x$dim > 4) seqq <- seq(4, x$dim, 4)
}

@@

  plot(density(y$Theta[, i]), 
       main = "", 
       axes = FALSE, 
       xlab = bquote(paste(theta[.(i)], " (", .(y$specs[i]), ")")),
       ylab = "", lwd = 2)
  axis(1)
  axis(2)
  coda::traceplot(y$Theta[, i], type = "l", xlab = "Iterations", ylab = "")
  coda::autocorr.plot(y$Theta[, i], auto.layout = FALSE)
  if (y$dim > 4) seqq <- seq(4, y$dim, 4)
}
